Improving the Replicability of Psychological Science Through Pedagogy

### 2016-09-23 paper/paper.Rmd
wang paper changes

This paper reported that the relationship between math anxiety and math performance follows an inverted-U pattern among college undergraduate students with higher intrinsic math motivation, whereas this same relationship is linearly negative among students with lower intrinsic math motivation. We targeted Study 2, the authors' own replication study, in which participants filled out three surveys about their math motivation and anxiety and completed a math task to measure performance. The key effect we targeted was the interaction of math anxiety squared and math motivation in predicting performance. We failed to find evidence for this effect. In contrast to the original study, we found a simple linear trend such that performance decreased with increasing math anxiety for both high and low math-motivation groups.

>>>>

This paper reported that the relationship between math anxiety and math performance follows an inverted-U pattern among college undergraduate students with higher intrinsic math motivation, whereas this same relationship is linearly negative among students with lower intrinsic math motivation. We targeted Study 2, the authors' own replication study, in which participants filled out three surveys about their math motivation and anxiety and completed a math task to measure performance. The key effect we targeted was the interaction of math anxiety squared and math motivation in predicting performance. We failed to find evidence for this effect. In contrast to the original study, we found a simple linear trend such that performance decreased with increasing math anxiety for both high and low math-motivation groups. Population differences provide one plausible explanation for the differences we found: Math performance was overall lower in our AMT sample than in the original undergraduate sample. It is possible that either the inverted U was undetectable given this lower level of performance, or that levels of motivation differed enough that the posited relationship did not hold.
